%%
%% Title Page — Biodiversity and Conservation (Springer Nature)
%%
\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\onehalfspacing

\begin{document}

\begin{center}

{\LARGE\bfseries Institutional fragility and climatic exposure drive\\[4pt]
biocultural vulnerability in traditional agricultural\\[4pt]
knowledge systems}

\vspace{24pt}

{\large
Catuxe Varj\~ao de Santana Oliveira\textsuperscript{a},\quad
Luiz Diego Vidal Santos\textsuperscript{b,*},\quad
Paulo Roberto Gagliardi\textsuperscript{a},\\[6pt]
T\^ania Cristina Azevedo\textsuperscript{c},\quad
Renisson Neponuceno de Ara\'ujo Filho\textsuperscript{d},\quad
Francisco Sandro Rodrigues Holanda\textsuperscript{e}
}

\vspace{18pt}

\end{center}

\noindent
\textsuperscript{a}\,Universidade Federal de Sergipe (UFS), Av.\ Marechal Rondon, s/n, Jardim Rosa Elze, S\~ao Crist\'ov\~ao, SE 49100-000, Brazil\\[4pt]
\textsuperscript{b}\,Universidade Estadual de Feira de Santana (UEFS), Av.\ Transnordestina, s/n, Novo Horizonte, Feira de Santana, BA 44036-900, Brazil\\[4pt]
\textsuperscript{c}\,Department of Applied Social Sciences, Universidade Estadual de Feira de Santana (UEFS), Feira de Santana, BA 44036-900, Brazil\\[4pt]
\textsuperscript{d}\,Department of Rural Technology, Universidade Federal Rural de Pernambuco (UFRPE), Rua Dom Manuel de Medeiros, s/n, Dois Irm\~aos, Recife, PE 52171-900, Brazil\\[4pt]
\textsuperscript{e}\,Department of Agronomic Engineering, Universidade Federal de Sergipe (UFS), Av.\ Marechal Rondon, s/n, Jardim Rosa Elze, S\~ao Crist\'ov\~ao, SE 49100-000, Brazil

\vspace{18pt}

\noindent
\textbf{*\,Corresponding author:}\\
Luiz Diego Vidal Santos\\
Universidade Estadual de Feira de Santana (UEFS)\\
Av.\ Transnordestina, s/n, Novo Horizonte\\
Feira de Santana, BA 44036-900, Brazil\\
E-mail: ldvsantos@uefs.br

\vspace{18pt}

\noindent
\textbf{ORCID:}\\[4pt]
Catuxe Varj\~ao de Santana Oliveira: 0000-0001-7276-4681\\
Luiz Diego Vidal Santos: 0000-0001-8659-8557\\
Paulo Roberto Gagliardi: 0000-0002-9394-8604\\
T\^ania Cristina Azevedo: 0000-0003-4242-4576\\
Renisson Neponuceno de Ara\'ujo Filho: 0000-0002-9747-1276\\
Francisco Sandro Rodrigues Holanda: --

\vspace{24pt}

\noindent
\textbf{Word count:} $\sim$5\,900 (main text, excluding references, tables, and figure captions)\\[4pt]
\textbf{Number of figures:} 7 (Figs.\ 1--7, with Fig.\ 7 comprising three sub-figures a--c)\\[4pt]
\textbf{Number of tables:} 2\\[4pt]
\textbf{Supplementary material:} Online Resource (separate document with 4 sections)

\vspace{24pt}
\hrule
\vspace{12pt}

\noindent\textbf{Acknowledgments}\\[4pt]
The authors thank the Universidade Federal de Sergipe (UFS) and the Universidade Estadual de Feira de Santana (UEFS) for the institutional and infrastructural support that enabled this research.

\vspace{12pt}

\noindent\textbf{Funding}\\[4pt]
This study was financed in part by the Coordena\c{c}\~ao de Aperfei\c{c}oamento de Pessoal de N\'ivel Superior -- Brazil (CAPES).

\vspace{12pt}

\noindent\textbf{CRediT authorship contribution statement}\\[4pt]
\textbf{Catuxe Varj\~ao de Santana Oliveira:} Conceptualization, Methodology, Investigation, Formal analysis, Data curation, Writing -- original draft.
\textbf{Luiz Diego Vidal Santos:} Methodology, Formal analysis, Validation, Writing -- review \& editing.
\textbf{Paulo Roberto Gagliardi:} Writing -- review \& editing, Supervision.
\textbf{T\^ania Cristina Azevedo:} Writing -- review \& editing.
\textbf{Renisson Neponuceno de Ara\'ujo Filho:} Writing -- review \& editing.

\vspace{12pt}

\noindent\textbf{Declaration of competing interests}\\[4pt]
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this article.

\vspace{12pt}

\noindent\textbf{Data availability}\\[4pt]
The extraction dataset, analysis scripts, and meta-analytic outputs are available on Mendeley Data (DOI: 10.17632/mh5sbx7ky7.1). The systematic review protocol is registered on the Open Science Framework (DOI: 10.17605/OSF.IO/HE8KT).

\end{document}
